Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-30 paper/ms.tex
A little bit of writing

\section{Simulated Data}\label{sec:simulated_data}
We now apply the method to two illustrative simulated images generated from
the above model. The true parameter values used are listed in
Table~\ref{tab:truth}. The broken power-law parameter values were chosen so that
roughly half of the stars' fluxes were below and above the break-point
respectively. Figure~\ref{fig:powerlaw} also shows the true flux distribution
used for the simulated images. Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars (including stars just outside of the image) and the second
image contains $\sim$1000 stars. The two simulated images
are shown in Figure~\ref{fig:simulated_data}.

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Test Case & Parameter & Value \\
\hline
1 & $N$ & 100\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.05\\
\hline
2 & $N$ & 1000\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.3\\
\hline
\end{tabular}
\end{center}
\caption{True parameter values used to generate the simulated data.
\label{tab:truth}}
\end{table}

@@

\section{Acknowledgements}
Marshall, Lang, Geraint, Wayne Stewart...

>>>>

\section{Simulated Data}\label{sec:simulated_data}
We now apply the method to two illustrative simulated images generated from
the above model. The purpose of this experiment was to test the computational
feasibility of the model, as well as to compare the inferences from the model
with those from more standard techniques.

The true parameter values for the two simulated data sets are listed in
Table~\ref{tab:truth}. The broken power-law parameter values were chosen so that
roughly half of the stars' fluxes were below and above the break-point
respectively. Figure~\ref{fig:powerlaw} also shows the true flux distribution
used for the simulated images. Each of the images
is $100 \times 100$ pixels in extent and covers a range from $-1$ to $1$ in
arbitrary units for both the $x$ and $y$ axes. The first image contains
$\sim$100 stars (including stars just outside of the image) and the second
image contains $\sim$1000 stars. The two simulated images themselves
are shown in Figure~\ref{fig:simulated_data}.

\begin{table}\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Test Case & Parameter & Value \\
\hline
1 & $N$ & 100\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.05\\
\hline
2 & $N$ & 1000\\
  & $h_1$ & 0.3\\
  & $h_2$ & 0.6\\
  & $\alpha_1$ & 1.1\\
  & $\alpha_2$ & 2\\
  & $\sigma$ & 0.3\\
\hline
\end{tabular}
\end{center}
\caption{True parameter values used to generate the simulated data. The main
difference between the two datasets is the number of stars.
\label{tab:truth}}
\end{table}

@@

\section{Acknowledgements}
It is a pleasure to thank Phil Marshall, Dustin Lang, and Geraint Lewis for
their comments on earlier versions of this work. BJB would also like to thank
Wayne Stewart and Arden Miller for their support during his first semester at
Auckland.
